%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[left=0.9in,top=1in,bottom=1in,right=1.1in]{geometry}

\usepackage{tikz}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItemUpdated}[1]{
  \item\small{
    {#1 \vspace{-7pt}}
  }
}

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textbf{{\small\textit{#3}}} & {\small \textit{#4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheading}[3]{
  \vspace{-1pt}
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} -- {\textit{#2}} & #3 \\
      % \textbf{{\small\textit{#3}}} & {\small \textit{#4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectSubheadingUpdated}[1]{
  \vspace{-1pt}
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} \\
      % \textbf{{\small\textit{#3}}} & {\small \textit{#4}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

% \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0pt]}
% \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\vspace{4pt}\huge Jaehong Lee (Jay)} & \textbf{Email} : \href{mailto:contact@jaehonglee.com}{contact@jaehonglee.com}\\
  \href{http://jaehonglee.com/}{jaehonglee.com \ExternalLink} {•} \href{http://github.com/jayhonglee/}{github.com/jayhonglee \ExternalLink} {•} \href{http://linkedin.com/in/jayhonglee/}{linkedin.com/in/jayhonglee \ExternalLink} &\textbf{Phone} : +1 (778) 984-5613 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  % \resumeSubHeadingListStart
    \resumeSubheading
      {Simon Fraser University}{Burnaby, BC}
      {Bachelor of Applied Science in Computer Engineering, Co-op (BASc)}{Sep. 2019 -- Aug. 2025}
      \resumeItemListStart
        \resumeItemUpdated
          {\textbf{Coursework}: computational optimization, statistical inference, probability theory, data analysis, algorithms, data structures, OOP, database systems, operating systems, software engineering, and multi-threading.}
      \resumeItemListEnd
  % \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}

    \resumeSubheading
      {Intersystem Controls, Inc.}{Vancouver, BC}
      {Software Engineering Intern -- Frontend}{Sep. 2021 - Dec. 2021}
      \resumeItemListStart
        \resumeItemUpdated
          {Led the design and development of a smart touch panel interface for a residential project at a Vancouver hotel. \href{https://github.com/jayhonglee/Jaehong-Lee-s-Resume/blob/main/img/Calista_UI1.jpg?raw=true}{\textbf{[Image]}}}
        \resumeItemUpdated
          {Created software solutions utilizing \textbf{HTML}, \textbf{CSS}, \textbf{JavaScript}, \textbf{React}, and \textbf{Redux}.}
        \resumeItemUpdated
          {Planned dynamic, user-friendly interfaces, managing app state for optimized user experience.}
        \resumeItemUpdated
          {Implemented \textbf{REST API} integration using \textbf{Postman} establishing communication with the backend systems.}
        \resumeItemUpdated
          {Conducted comprehensive unit testing using \textbf{Jest} to ensure modularization and robustness of components.}
        \resumeItemUpdated
          {Developed a configurable module, reducing manual input by \textbf{80\%}, establishing scalable architecture for future projects.}
        \resumeItemUpdated
          {Collaborated closely with a UX/UI designer to optimize user functionality and plan the interface design, ensuring seamless integration of user experience principles into the smart touch panel interface.}
        \resumeItemUpdated
          {Participated in intern interviews, evaluating candidates, contributing to the team's growth and  transition planning.}
      \resumeItemListEnd

%-----------PROJECTS-----------------
\section{Selected Projects}
 \projectSubheading
      {\href{https://grabpencil.com/}{GrabPencil.com \ExternalLink}}{Solo Project}{\textit{\small Sep. 2023 -- Present}}
      \resumeItemListStart
        \resumeItemUpdated
          {Created a tutoring platform for university students using \textbf{React}, \textbf{Node.js}, \textbf{Express.js}, \textbf{MongoDB}, and \textbf{Mongoose}.}
        \resumeItemUpdated
          {Developed a database search feature with comprehensive filters for easier tutor finding experience.}
        \resumeItemUpdated
          {Created \textbf{Node.js}-based backend \textbf{REST API} enabling CRUD operations for tutoring job postings.}
        \resumeItemUpdated
          {Implemented user authentication, encompassing password hashing and \textbf{JWT}-based authentication with cookie storage.}
        \resumeItemUpdated
          {Utilized \textbf{Socket.io} for real-time communication, including online user tracking, and stored chat history in \textbf{MongoDB}.}
        \resumeItemUpdated
          {Incorporated \textbf{Bootstrap} for streamlined and responsive frontend design.}
        \resumeItemUpdated
          {Conducted backend API endpoint testing using \textbf{Jest} and \textbf{Supertest} for comprehensive validation and reliability.}
      \resumeItemListEnd
      
 \vspace{6pt}\projectSubheading
      {\href{https://github.com/jayhonglee/Hardware-Aware-Software-Optimization}{Hardware-Aware Software Optimization \ExternalLink}}{Pair Academic Term Project}{\textit{\small Jul. 2023}}
      \resumeItemListStart
        \resumeItemUpdated
          {Optimized the General Matrix Multiply algorithm on a 10-core X86 CPU using \textbf{C} for increased efficiency.}
        \resumeItemUpdated
          {Employed data tiling optimization with a tile size of 16, achieving a speedup of \textbf{8.56x}.}
        \resumeItemUpdated
          {Implemented X86 SIMD intrinsics for vectorization with data tiling, resulting in a \textbf{61.94x} speedup.}
        \resumeItemUpdated
          {Applied OpenMP multithreading for parallelization, with data tiling and vectorization, achieving a \textbf{515.35x} speedup.}
        \resumeItemUpdated
          {Integrated loop unrolling with the three optimizations, resulting in a \textbf{649.53x} speedup (\textbf{8 minutes} to \textbf{0.739 seconds}).}
      \resumeItemListEnd
      
 \vspace{6pt}\projectSubheading
      {\href{https://github.com/jayhonglee/mazeGame}{Maze Game \ExternalLink}}{Team Academic Term Project}{\textit{\small Apr. 2023}}
      \resumeItemListStart
        \resumeItemUpdated
          {Developed a \textbf{Java} game app with \textbf{Maven} for project management, using \textbf{OOP} principles for robust and scalable code.}
        \resumeItemUpdated
          {Implemented pathfinding algorithm for enemy movement optimization.}
        \resumeItemUpdated
          {Utilized Scrum process model for efficient project management and iterative development.}
        \resumeItemUpdated
          {Employed \textbf{JUnit} for unit testing and conducted line and branch coverage testing to validate code effectiveness.}
      \resumeItemListEnd
      

%
%--------PROGRAMMING SKILLS------------
\section{Certificates}
 \projectSubheadingUpdated
      {Udemy Online Courses}
      \resumeItemListStart
        \resumeItemUpdated
          {\textbf{\href{https://www.udemy.com/course/understand-javascript/}{JavaScript: Understanding the Weird Parts \ExternalLink}} \hfill \textit{Dec. 2023}}
        \resumeItemUpdated
          {\textbf{\href{https://www.udemy.com/course/the-complete-nodejs-developer-course-2/}{The Complete Node.js Developer Course (3rd Edition) \ExternalLink}} \hfill \textit{Feb. 2023}}
        \resumeItemUpdated
          {\textbf{\href{https://www.udemy.com/course/the-complete-javascript-course/}{The Complete JavaScript Course 2024: From Zero to Expert! \ExternalLink}} \hfill \textit{May 2021}}
        \resumeItemUpdated
          {\textbf{\href{https://www.udemy.com/course/modern-html-css-from-the-beginning/}{Modern HTML \& CSS From The Beginning (Including Sass) \ExternalLink}} \hfill \textit{Sep. 2020}}
       \resumeItemListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
   \resumeItemListStart
        \resumeItemUpdated
          {\textbf{Languages}{: HTML, CSS, JavaScript, C, C++, Java, SQL, MATLAB, VHDL, \LaTeX }}
        \resumeItemUpdated
          {\textbf{Frameworks and Libraries}{: Node.js, React.js, Redux, Express.js, Mongoose, Bootstrap, Jest, JUnit }}
        \resumeItemUpdated
          {\textbf{Technologies and Tools}{: Git, Unix/Linux, MongoDB, NoSQL, Bash, Heroku, Render}}
   \resumeItemListEnd


%-------------------------------------------
\end{document}
